sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-09-08 doc/paper-jss/sdmTMB-cover.tex
Update cover letter

\documentclass[letterpaper]{letter}
\usepackage[margin=1.55in]{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\addtolength{\topmargin}{-30pt}
\addtolength{\textheight}{55pt}

@@

Thank you for considering our manuscript for publication in the Journal of Statistical Software. This is a revised version of manuscript 4939 after receiving the following editor comments with an encouragement to resubmit:

\begin{quote}
\input{editor-comments0}
\end{quote}

We apologize for not better dealing with the GitHub-only package \pkg{sdmTMBextra}. Indeed, this was originally a part of the main package. We had just split this functionality out of the main package because of valgrind/gcc-ASAN check errors on CRAN that could not be replicated or resolved. This also had the benefit of substantially reducing the number of package dependencies for the main CRAN package. We have now omitted the corresponding code in the appendix and referenced the vignette on residuals for further details.

@@

Speed: The package combines the SPDE approximation with estimation in the \pkg{TMB} \proglang{R} package for computational efficiency. Across our comparisons, \pkg{sdmTMB} was 6--24 times faster than the \pkg{INLA} or \pkg{inlabru} packages---the software with the most similar capabilities for this class of models.

As evidence of its utility, there are already \href{https://github.com/pbs-assess/sdmTMB/wiki/Publications-using-sdmTMB}{16 published preprints, papers, or reports} using \pkg{sdmTMB}, six funded research grants, an ever-growing number of ongoing research projects, and international workshops that in total have been attended by $>$200 participants.

@@

\vspace{3mm}
\closing{Sincerely,\\
\fromsig{\includegraphics[scale=0.42]{/Users/seananderson/Dropbox/sig.pdf}}
}

>>>>

\documentclass[letterpaper]{letter}
\usepackage[margin=1.43in]{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\addtolength{\topmargin}{-20pt}
\addtolength{\textheight}{75pt}

@@

Thank you for considering our manuscript for publication in the Journal of Statistical Software. We have made all the requested editorial changes as described in the file \texttt{formatting-response.pdf}.

@@

Speed: The package combines the SPDE approximation with estimation in the \pkg{TMB} \proglang{R} package for computational efficiency. Across our comparisons, \pkg{sdmTMB} was 7--30 times faster than the \pkg{INLA} or \pkg{inlabru} packages---the software with the most similar capabilities for this class of models.

As evidence of its utility, there are already \href{https://github.com/pbs-assess/sdmTMB/wiki/Publications-using-sdmTMB}{19 published preprints, papers, or reports} using \pkg{sdmTMB}, six funded research grants, an ever-growing number of ongoing research projects, and international workshops that in total have been attended by $>$200 participants.

@@

\vspace{2mm}
\closing{Sincerely,\\
\fromsig{\includegraphics[scale=0.3]{/Users/seananderson/Dropbox/sig.pdf}}
}
